\documentclass{article}

\usepackage{indentfirst}

\begin{document}

\section{A}

Some factors to consider when deciding which type of slot machine to build
are how much people enjoy games in the category, how difficult the odds are to calculate; especially after modifications to he game are made.  Another factor to consider is how much time, and how difficult implimentation may be.

From personal observation, it seems that the most enjoyed slot games are reel slots and playing card slots. This is most likely the reason these two types of games exist with the greatest numbers.  However, it is also important to remember that not everybody that plays slots enjoys the same slot machines.  The second factor, having to do with calculating odds seems to be easiest for reel games.  Games with playing cards like blackjack can be very difficult to calculate true odds on.  For example when the book "Beat the Dealer" came out, it actually showed that the player could put the odds in their own favor simply by varying the bets.  By making sure that the deck is shufled between hands, the odds get much easier to calculate, so this is not a great concern.  Another issue with playing card games is that because they all have different rules, a great deal of research would be involved to determine what types of card games people like and dislike.  This could cause problems in the design phase because of the amount of deadline for the design phase.

Because the reel type slot machines are faster  



\end{document}
