%\section{Introduction}
  For this project, the team I was assigned to consisted of myself, Krysta Pascual, and Erin Keith.  This team worked together very well and was able to complete the project in timely fashion.  Each team member also completed approximately the same amount of work on the final project.

    Our team met together only one time outside class.  This meeting took place in the Engineering Computing Center on Sunday, November 14 from 1:00 and 2:00 in the afternoon. During this meeting the initial roles of each team member were decided.  My job was to implement the graphical portion of the project. Krysta was given the task of creating the artwork used for the symbols as well as implementation of the menu.  Erin took the task of implementing the cryptographic pseudo-random number generator and also she was assigned to take care of any other coding that may come up in the future.  Because we choose to use Erin's idea of a  “Create Your Own Adventure”, she was also given the task of answering any design issues that may arise. 
      Some time after this meeting, via e-mail the decision to remove the user interface was made. After completing the graphical user interface, it seemed unreasonable to have a separate menu.  Because of this, Krysta was given the task of creating the functions which controlled the credits, wins and losses. This also included determining which symbols the payline read based on the position of the reels.  Although we had planned on future meetings, because of clashing schedules this became nearly impossible.  To make up for the lack of physical contact, all team members communicated over e-mail regularly.

        There was a bit of confusion after the first meeting which was resolved before class on the 18th of November.  The confusion which I discussed with Erin was how many symbols needed to be fabricated.  From what I understood, there would be multiple scenarios, each with its own set of symbols.  What Erin had actually meant was that there would be only one set of symbols which encompassed all the different scenarios, or one symbol per scenario.  This was an important issue because I would be implementing the graphics. With multiple scenarios I would need to build in functionality to easily switch between texture sets.  It turned out that I needed to implement this functionality anyway in order to allow multiple resolutions of the same texture to be loaded.

          Erin and I also met informally on November 24, so that I could demonstrate how the current implementation worked.  We also discussed how the demo would be handled because I would be at the ISVC conference on the December 1 when the demos were to take place.

\section{E-mails}
\begin{itemize}
\item
            {\bf Nov 12} Erin notified Krysta and I that she would not be able to meet Friday, so we decided to meet Sunday.
\item              {\bf Nov 14} Erin e-mailed us her design document following the meeting.
\item                {\bf Nov 17/18} The team discussed plans to meet Friday, but because ACM went to Google, Erin was not available so this was cancelled.
\item                  {\bf Nov 22} I sent the first draft of the slot machines graphical implementation along with some function prototypes dealing with calculating credits and win amounts that still needed to be implemented.
\item                    {\bf Nov 27} Erin asked about how I was implementing the random numbers, I replied that I was using the built in random number generator for now, but would change that when her pseudo-random number generator was completed.
\item                     {\bf Nov 28} Krysta questioned what she needed to do on the menu screen, we decided that it was not necessary and she would implement the credits and win amounts functions instead.
\item                        {\bf Nov 29} Krysta sent the finished functions as well as the completed reel textures. Erin sent the completed psudo-random number generator.  I replied to let them know I would be putting the program together that evening.
\item                          {\bf Nov 30} I sent the completed program with all the functions and textures added.

\end{itemize}
