\section{Introduction}
When writing a design proposal, there are some key ideas to keep in mind to be successful. This 
critique will use these ideas in order to determine a fair grade for the paper out of 100 points.
The grading is split into three categories.  The first category which is 30\% of the grade, scales 
how well the write-up was written. In this category, points will be deducted for mistakes in 
grammar, spelling, and clarity.  Although spelling and grammar are straightforward, points for 
clarity can be deducted for informal prose, mixing tenses, ambiguity, flowery language,
excessive use of ``and'', ``or'', and ``but'', non-testable claims, and inconstant terminology.
Another aspect of the write-up category is how well the paper is structured.  This paper should
be structured in such a way that it contains at least an introduction, a body, and a conclusion.
The second category which is also 30\% of the grade, will represent how well the overall project 
description was explained.  The last category which is the remaining 40\% of the grade, represents the how
well the design and plans were described.

\section{Proposed design plans}
The design that was given to me, proposes a video slot machine which is based on the game
of memory.  Memory is a game where a player is given a board of face-down tiles, and then
asked to turn over two at a time.  If the two face-up tiles match, then the player wins a
prize and the matching tiles are removed.  If the two face-up tiles do not match, then the
tiles are turned face-down again.  The player repeats this process until the all of the tiles
have been removed.  In the proposed rendition of the game, rather than allowing the player to collect
all the prizes on the board, an allotted number of turns are given and/or a time limit is used
(unclear).  When a player matches two tiles, they receive the amount of money indicated on
the tile.  Because of clarity issues mentioned in the write-up section, it is impossible to
tell if the memory game is simply a bonus round game for another slot machine, or if it is
itself the video slot machine.  If it is the video slot machine, then the bonus round that
is mentioned is never discussed.  However if it is the bonus round, the actual video slot
machine is never discussed.  Because of this five points are deducted from the design.

In the instructions for the project, the design document document is supposed to ``discuss
alternative solutions and clearly specify tradeoffs''.  In the ``Implementation Details'' section,
methods in which the free variables can be modified are discussed.  However, no alternative solutions
or implementation issues are discussed in this paper great depth.  For this reason another five points
will be deduced from this section.


\section{Write-up}
The author of this paper did not misspell any words, nor did they have poor grammar. For this
reason alone, I will award 15 points.  The structure of the design does include an introduction,
body, and conclusion.  However these sections are disproportional to each other.  The
introduction and thesis are nearly a page and a half long, while the body of the paper is only
a half of a page.  For this reason 3 of the 5 points for structure are awarded.

\subsection{Clarity}

The paper is fairly
clear, but there are some parts that needed to be explained more clearly.

In the second paragraph of
the section labeled ``Game Abstract'', the second sentence seems to imply that the entire game
is only the bonus round.  If this is true, then nowhere in the paper is the normal play of this
game discussed.  I have deemed this to be an incomplete thought that was left in the paper due to
carelessness. Because of this, one point will be taken off the total for clarity.

In the first paragraph of
the Abstract, inconsistent terminology is used.  The first time that choosing tiles is mentioned,
the word ``choose'' is used, however two sentences later, the author uses ``select''.  This is
one more point off of the clarity score.

Another unclear idea in the abstract is how the game
ends.  In the first section the game of memory is described as ``repeats until there are no tiles
left'', while in the next paragraph, the game is played for ``the allotted number of turns''.
Furthermore, in the implementation section, ``a time limit is imposed''.  It is unclear which one
or more of these methods is used to end the game. For this lack of clarity, two points are deducted.

Another unclear part of the abstract is where the author states
that ``the grid can be selected to the appropriate size''.  The ``can be'' part of this statement
is ambiguous because it implies that the grid might not be selected to the appropriate size.
This same statement also begs the question of who or what will be selecting the size, and what
exactly is the appropriate size.  One point is deducted for this unclear statement.  Because of
these mistakes, 5 out of 10 points are awarded for clarity.

\section{Explanation of project description}
The project description was explained in it's own section titled ``Project Introduction''.  The explanation
is clear, and allows any competent reader to easily get an understanding of what is expected out of this
project.  Because of this, all the points for the explanation of the project description are awarded.

